Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2015-07-14 Papers/InProgress/HajekAndersonControversy/main.tex
Move definitions from footnotes to main text.

For both \textbf{constant domain semantics} and \textbf{varying domain
semantics}, the following results hold for \emph{Anderson's
Emendation} (cf. Fig. \ref{fig:Anderson}): T1, C
and T3' can be quickly automated (in logics \K, \K and \KB,
respectively); the axioms A4 and A5' are proven redundant\footnote{
An axiom $A$ is redundant w.r.t. a set of axioms $S$ iff $A$ is
entailed by $S$.  } (the former in logic \KFourB and the latter
already in \K); a trivial countermodel (with two worlds and  two
individuals) for MC is generated by Nitpick (for all mentioned
logics); all axioms and definitions are shown to be mutually
consistent.

@@

The redundancy of A4 and A5 is particularly controversial. Magari
\cite{Magari1988} claimed that A4 and A5 are superfluous\footnote{
An axiom $A$ is superfluous w.r.t. a set of axioms $S$ iff T3 is
entailed by $S \setminus \{ A \}$. }, arguing that T3 is true in all
models of the other axioms and definitions by Gödel.
\citet[p.~5-6]{Hajek_Magari_and_others_1996} investigated this
further, and claimed that Magari's claim is not valid, but is
nevertheless true  under additional silent assumptions by Magari.
Moreover, \citet[p.~2]{Hajek_Magari_and_others_1996} cites his earlier
work\footnote{Although \citep{Hajek_der_Mathematiker_2001} precedes
\citep{Hajek_Magari_and_others_1996} in writing, it was published only
5 years later, in German.} \citep{Hajek_der_Mathematiker_2001}, where
he claims (in Theorem 5.3) that for Anderson's emended theory
\citep{anderson90:_some_emend_of_goedel_ontol_proof}, A4 and A5 are
not only superfluous, but also redundant. \citet[footnote 1 in
p.~1]{AndersonGettings}, in a footnote, rebutted Hájek's claim,
arguing that the redundancy of A4 and A5 holds only under constant
domain semantics, while Anderson's emended theory ought to be taken
under Cocchiarella's semantics \citep{Cocchiarella} (a varying domain
semantics). Our results show that Hájek was originally right, under
both constant and varying domain semantics.

>>>>

\begin{definition}
An axiom $A$ is \textbf{redundant} w.r.t. a set of axioms $S$ iff $A$ is
entailed by $S$. \end{definition}

For both \textbf{constant domain semantics} and \textbf{varying domain
semantics}, the following results hold for \emph{Anderson's
Emendation} (cf. Fig. \ref{fig:Anderson}): T1, C
and T3' can be quickly automated (in logics \K, \K and \KB,
respectively); the axioms A4 and A5' are proven redundant (the former in logic \KFourB and the latter
already in \K); a trivial countermodel (with two worlds and  two
individuals) for MC is generated by Nitpick (for all mentioned
logics); all axioms and definitions are shown to be mutually
consistent.

@@

\begin{definition}
An axiom $A$ is \textbf{superfluous} w.r.t. a set of axioms $S$ iff T3 is
entailed by $S \setminus \{ A \}$.
\end{definition}

The redundancy of A4 and A5 is particularly controversial. Magari
\cite{Magari1988} claimed that A4 and A5 are superfluous, arguing that T3 is true in all
models of the other axioms and definitions by Gödel.
\citet[p.~5-6]{Hajek_Magari_and_others_1996} investigated this
further, and claimed that Magari's claim is not valid, but is
nevertheless true  under additional silent assumptions by Magari.
Moreover, \citet[p.~2]{Hajek_Magari_and_others_1996} cites his earlier
work\footnote{Although \citep{Hajek_der_Mathematiker_2001} precedes
\citep{Hajek_Magari_and_others_1996} in writing, it was published only
5 years later, in German.} \citep{Hajek_der_Mathematiker_2001}, where
he claims (in Theorem 5.3) that for Anderson's emended theory
\citep{anderson90:_some_emend_of_goedel_ontol_proof}, A4 and A5 are
not only superfluous, but also redundant. \citet[footnote 1 in
p.~1]{AndersonGettings}, in a footnote, rebutted Hájek's claim,
arguing that the redundancy of A4 and A5 holds only under constant
domain semantics, while Anderson's emended theory ought to be taken
under Cocchiarella's semantics \citep{Cocchiarella} (a varying domain
semantics). Our results show that Hájek was originally right, under
both constant and varying domain semantics.
